Reproduction frequency and offspring survival decline in elephant seals past prime age

### 2024-07-19 paper/paperv3.qmd
sex ratio 1, 2 tail p vals

# Are hypotheses supported by the model?
extract_p <- \(h) map_dbl(mod_sens, \(m) pnorm(m[[h]]["age10:age_catOld", "z value"]))
p_tbl <- tibble(age_cutoff = cutoff, 
                "H1 (breeding)" = extract_p("h1"),
                "H2a (survival)" = extract_p("h2_surv"),
                "H2b (recruitment)" = extract_p("h2_recr"),
                "H3 (sex ratio)" = extract_p("h3") * 2)

@@

p_tbl %>% 
  pivot_longer(-age_cutoff, names_to = "hypothesis", values_to = "p") %>%
  ggplot(aes(age_cutoff, p)) +
  geom_point() +
  geom_hline(yintercept = 0.05, linetype = "dashed") +
  geom_text(aes(x, y, label = tag),
            tibble(hypothesis = colnames(p_tbl)[-1],
                   tag = LETTERS[1:4],
                   x = 8, y = 3),
            vjust = 1,
            fontface = "bold") +
  scale_y_log10(labels = scales::number) +
  labs(x = "Senescence onset (years)") +
  expand_limits(y = 3) +
  facet_wrap(~hypothesis)

>>>>

# Are hypotheses supported by the model?
extract_p <- function(h, tails = 1) {
  if (tails == 1) {
    map_dbl(mod_sens, \(m) pnorm(m[[h]]["age10:age_catOld", "z value"]))
  } else if (tails == 2) {
    map_dbl(mod_sens, \(m) 2 * pnorm(m[[h]]["age10:age_catOld", "z value"],
                                     lower.tail = FALSE))
  } else {
    stop("tails must be 1 or 2")
  }
}
p_tbl <- tibble(age_cutoff = cutoff, 
                "H1 (breeding)" = extract_p("h1"),
                "H2a (survival)" = extract_p("h2_surv"),
                "H2b (recruitment)" = extract_p("h2_recr"),
                "H3 (sex ratio)" = extract_p("h3"),
                "H3 (sex ratio; 2 tail)" = extract_p("h3", tails = 2))

@@

p_tbl %>% 
  pivot_longer(-age_cutoff, names_to = "hypothesis", values_to = "p") %>%
  mutate(hypgrp = ifelse(str_detect(hypothesis, "H3"), 
                         "H3 (sex ratio)", 
                         hypothesis)) %>% 
  ggplot(aes(age_cutoff, p)) +
  geom_point(aes(color = hypothesis == "H3 (sex ratio; 2 tail)")) +
  geom_hline(yintercept = 0.05, linetype = "dashed") +
  geom_text(aes(x, y, label = tag),
            tibble(hypgrp = colnames(p_tbl)[2:5],
                   tag = LETTERS[1:4],
                   x = 8, y = 3),
            vjust = 1,
            fontface = "bold") +
  scale_y_log10(labels = scales::number) +
  scale_color_manual(values = c("black", "grey50")) +
  labs(x = "Senescence onset (years)") +
  expand_limits(y = 3) +
  facet_wrap(~hypgrp) +
  theme(legend.position = "none")
